MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
Added anaysis on accuracy

@@

# Reshape the dataframe

game <- cast(data = df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + LOCATION + player_name + W ~ FGM)

# Field Goal Attempts

game[, "FGA"] <- NA
for(i in 1:nrow(game)){
  game[i, "FGA"] <- game[i, "1"] + game[i, "0"]
}

# find Feild Goal % of each indivudual player in that match

game[, "FG%"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG%"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}

@@

#Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
#FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
#for(i in 21400001:21400908){
#  j = i - 21400001 +1 # 
#  game <- df[, df[, "GAME_ID1"] == i]
#  home <- game[, game["LOCATION"] == "H"]
#  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
#  away <- game[, game["LOCATION"] == "A"]
#  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
#  FG_Percentage[j] <- home.p
#  FG_Percentage[j + 1] = away.p
#  Team[j] = "H"
#  Team[j + 1] = "A"
#}

>>>>

#Close Game Effect (Justin)

```{r}
# create new variable to seperate overtime

df[, "OVERTIME"] <- as.numeric()

for (i in 1:nrow(df)) {
  if (df[i, "PERIOD"] >= 5) df[i, "OVERTIME"] <- 1
  if (df[i, "PERIOD"] <= 4) df[i, "OVERTIME"] <- 0
}

# accuracy 
acc_ot <- as.numeric
acc_ot <- sum(df$OVERTIME == 1 & df$FGM == 1)/sum(df$OVERTIME == 1)

acc_qrt1 <- as.numeric
acc_qrt1 <- sum(df$PERIOD == 1 & df$FGM == 1)/sum(df$PERIOD == 1)

acc_qrt2 <- as.numeric
acc_qrt2 <- sum(df$PERIOD == 2 & df$FGM == 1)/sum(df$PERIOD == 2)

acc_qrt3 <- as.numeric
acc_qrt3 <- sum(df$PERIOD == 3 & df$FGM == 1)/sum(df$PERIOD == 3)

acc_qrt4 <- as.numeric
acc_qrt4 <- sum(df$PERIOD == 4 & df$FGM == 1)/sum(df$PERIOD == 4)

acc_qrt5 <- as.numeric
acc_qrt5 <- sum(df$PERIOD == 5 & df$FGM == 1)/sum(df$PERIOD == 5)

acc_qrt6 <- as.numeric
acc_qrt6 <- sum(df$PERIOD == 6 & df$FGM == 1)/sum(df$PERIOD == 6)

acc_qrt7 <- as.numeric
acc_qrt7 <- sum(df$PERIOD == 7 & df$FGM == 1)/sum(df$PERIOD == 7)

acc_qrt1_4 <- as.numeric
acc_qrt1_4 <- sum(df$PERIOD <= 4 & df$FGM == 1) / sum(df$PERIOD <= 4)

t.test(df$FGM[df$PERIOD <= 4], df$FGM[df$PERIOD >= 5])
t.test(df$FGM[df$PERIOD == 1], df$FGM[df$PERIOD == 2])
t.test(df$FGM[df$PERIOD == 2], df$FGM[df$PERIOD == 3])
t.test(df$FGM[df$PERIOD == 3], df$FGM[df$PERIOD == 4])
t.test(df$FGM[df$PERIOD == 1], df$FGM[df$PERIOD == 3])
t.test(df$FGM[df$PERIOD == 2], df$FGM[df$PERIOD == 4])

# accuracy for Shot Clock

  # dealing with missing values
df[, "SHOT_CLOCK_NONA"] <- df[, "SHOT_CLOCK"]
is.na(df$SHOT_CLOCK_NONA) <- 99

acc_sec24 <- as.numeric
acc_sec24 <- sum(df$SHOT_CLOCK > 23 & df$FGM == 1) / sum(df$SHOT_CLOCK > 23)

@@

# Trying to reshape...

library(reshape)
game <- cast(data = df, GAME_ID1 ~ SHOT_RESULT)
View(game)

@@

Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
for(i in 21400001:21400908){
  j = i - 21400001 +1 # 
  game <- df[, df[, "GAME_ID1"] == i]
  home <- game[, game["LOCATION"] == "H"]
  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
  away <- game[, game["LOCATION"] == "A"]
  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
  FG_Percentage[j] <- home.p
  FG_Percentage[j + 1] = away.p
  Team[j] = "H"
  Team[j + 1] = "A"
}
